Verifying Demonstrations

### 2018-11-01 paper/system-model.tex
Adds comment on CA and Sybil attacks

Throughout this paper, each time we refer to a participant, such as Alice, we actually mean a personal device that can perform cryptographic operations and communicate with other local devices on Alice's behalf. 
Furthermore, we assume that each participant has a digital certificate signed by the \ac{CA}.
For instance, we could use the cryptographic keys of any national electronic identity system, identity card or passport.
This assumption is needed to prevent Sybil attacks~\cite{SybilAttack}, which would have a disastrous effect on the crowd-counting estimation.

>>>>

Throughout this paper, each time we refer to a participant, such as Alice, we actually mean a personal device that can perform cryptographic operations and communicate with other local devices on Alice's behalf. 
Furthermore, we assume that each participant has a digital certificate signed by the \ac{CA}.
For instance, we could use the cryptographic keys of any national electronic identity system, identity card or passport.
This assumption is needed to prevent Sybil attacks~\cite{SybilAttack}, which 
would have a disastrous effect on the crowd-counting estimation\footnote{%
  Of course, this means that the \ac{CA} can perform a Sybil attack on the 
  system.
  So, if the \ac{CA} is controlled by the government, then no counts in favour 
  of the government can be be trusted.
}.
